MSDS6372Project1

### 2021-02-02 MSDS6372Project1.Rmd
add validation result 2

>>>>

# Validation test between best models under each objective

```{r}
validate.result = validate$MSRP
validate = validate[,-15]
# Validate best model from objective 1 result
objective1.predict = predict(log.model7,validate)
objective1.predict = exp(objective1.predict)
# See forward test ASE
validateMSE_Object1 <- mean((validate.result-objective1.predict)^2)
sqrt(validateMSE_Object1) #test RMSE = 21896.2

# Validate best model from objective 2 result
objective2.reg.predict = predict(lasso.lm.log,validate)
objective2.reg.predict = exp(objective2.reg.predict)
validateMSE_object2.reg.predict = mean((validate.result-objective2.reg.predict)^2)
sqrt(validateMSE_object2.reg.predict) #test RMSE = 5521.819

# Validate best model from KNN
validateKNN = validate[,-c(1,2,4,7,8,10,11,15,16,17,18,19,20,21,22,23,24,25)]
objective2.knn.predict = predict(fit,validateKNN)
validateASE_KNN_k2 = mean((validate.result-objective2.knn.predict)^2)
sqrt(validateASE_KNN_k2) # test RMSE = 5718.328
